A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2019-05-24 writeUp/supplementary_materials_methods.tex
Rejigged layout of repo and added to-do

\subsubsection{Analysis of censored data series}\label{sec:dissection_censored}
In some of the published papers the data are censored above a threshold age, $a_T$. In these cases we only know the number, $y(a_T)$, of individuals who were captured and dissected with an estimated physiological age that is greater than or equal to the threshold. Since we do not know the estimated physiological age of individual specimens $i$, we represent this as a parameter, $\aleph_i$, in our statistical model. This means that the joint distribution is a function of $y(a_T)$ different $\aleph_i$ parameters. Since these parameters are not directly of interest, and our chosen MCMC engine, Stan \citep{stan-software:2014}, does not directly allow discrete parameters in models, we marginalise these out of the joint distribution. To do this exactly would require an infinite sum over all the possible ages for all $y(a_T)$ mosquitoes that have been caught whose age exceeds the threshold. Rather than carry out this intractable number of summations we instead make the approximation that all mosquitoes in this group are of the same age $\aleph_i = \aleph,\; \forall i \in (1,...,y(a_T))$. We believe this assumption is justifiable, particularly since the numbers of mosquitoes in each subsequent age category is a strongly-decreasing function of age. This means that whilst we do not know with certainty individuals' ages, it is likely that most will be of the threshold age $a_T$.

@@

Using the collected data, we estimated that uncertainty in the first gonotrophic cycle duration is estimated as $\mathcal{N}(4.26, 0.38)$ and, for subsequent cycles, $\mathcal{N}(3.85, 0.35)$.

>>>>

\subsubsection{Analysis of censored data series}\label{sec:dissection_censored}
Some published studies do not distinguish the number of gonotrophic studies
beyond a threshold, $a_T$ (the more ovariole dilations there are the harder it
is to count them) which is akin to censoring the data. This
censoring involves only a relatively small number of mosquitoes in each
time series (median = 2\%) and so we are confident that these few cases do not substantially affect our inferences. We, however, now describe the statistical model used to describe these instances. In these cases we only know the number, $y(a_T)$, of individuals who were captured and dissected with an estimated physiological age that is greater than or equal to the threshold. Since we do not know the estimated physiological age of individual specimens $i$, we represent this as a parameter, $\aleph_i$, in our statistical model. This means that the joint distribution is a function of $y(a_T)$ different $\aleph_i$ parameters. Since these parameters are not directly of interest, and our chosen MCMC engine, Stan \citep{stan-software:2014}, does not directly allow discrete parameters in models, we marginalise these out of the joint distribution. To do this exactly would require an infinite sum over all the possible ages for all $y(a_T)$ mosquitoes that have been caught whose age exceeds the threshold. Rather than carry out this intractable number of summations we instead make the approximation that all mosquitoes in this group are of the same age $\aleph_i = \aleph,\; \forall i \in (1,...,y(a_T))$. We believe this assumption is justifiable, particularly since the numbers of mosquitoes in each subsequent age category is a strongly-decreasing function of age. This means that whilst we do not know with certainty individuals' ages, it is likely that most will be of the threshold age $a_T$.

@@

Using the collected data, we estimated that the first gonotrophic cycle duration was $\mathcal{N}(4.26, 0.38)$ and, for subsequent cycles, $\mathcal{N}(3.85, 0.35)$.
